systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2005-11-08 paper/trunk/systemfit_summary.tex
just changed some line breaks (deleted new ones and restored deleted ones) to make it easier to find the changes that Jeff committed in the last revision(s)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@582 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added serial correlation and heteroscedastic paragraph
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@585 591db2bd-e0a0-4d22-8c19-2192dbb7da31

>>>>

For all of the methods developed in the package, the disturbances of
the individual equations are assumed to be independent and identically
distributed (iid) and the models are fit using least squares.  
The package could be enhanced by the inclusion of methods to fit
equations with serially correlated and heteroscedastic disturbances.
